### 2023-04-24 paper-reviews/papers-2023.tex
Add MPI communication paper

>>>>

\section*{Parallel Programming}
\begin{itemize}
    \item \cite{Thakur:MPIOptimization:2005}:

    The article presents different high-performance implementations of collective MPI operations. The authors assume that the time to send similar package between any two nodes is the same and does not depend on number of concurrent communications. This is a very simple cost model but seems to be sufficient for the author's needs. The article is a good source for different one-to-all, all-to-one, all-to-all communication algorithms. Interesting but expected idea from the article is to use different communication algorithms depending on message size.
\end{itemize}
